---
title: "*ZOLL* Data Analysis" 

knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))}) 
 
author: 
  - "**Kelle Lewis RN BSN TCRN**"
  - "Kelle.Lewis@renown.org"
  - "Professional Advancement for Clinical Excellence"
  - "2020"
output: html_document
---

```{r include=FALSE}

### Initialization

if (!require(pacman)) {install.packages('pacman')} #install pacman if it is not loaded
#pacman is a package load/install handler
library(pacman)

pacman::p_load(
  'tidyverse', # for data manipulation 
  'ggplot2', # for exhibits
  'lubridate', # for date manipulation
  'ggthemes', # plot themes
  'knitr',
  'kableExtra',
  'DT'
               )
#set wd
setwd("C:/Users/pc/Desktop/drive_0/Desktop/Renown PACE")

zollData <- read_csv("High Performance Code Team - csv export.csv") %>%
  mutate(Date = mdy(Date)) %>%
  arrange(Date)
zollData <- zollData %>%
  mutate(record = 1:nrow(zollData),
         md = paste(str_pad(string = paste(record,"_",sep = ""),
                            width = 4, side = "right", 
                            pad = "_"),str_pad(string = paste(month(Date),"/",day(Date),sep = ""),width = 7 ,side = "left",
                                               pad = "_"),sep = ""))

zollData <- zollData %>%
  mutate(md = factor(md,levels = unique(zollData$md)))

```

```{r include=FALSE}
#plot functions

percentBars <- function(varName, data = zollData, goal = .8, newName = NA) {
  if(!is.na(newName)){
    if(newName %in% names(data)){
      data <- data %>% select(-!!as.symbol(newName))
    }
    data <- data %>% rename(!!as.symbol(as.name(newName)) := !!as.symbol(varName))
    varName <- newName
  }

dataValues <- data %>% select(!!as.symbol(varName)) %>% unlist() %>% na.omit()

data <- data %>% 
  mutate(fi = if_else(!!as.symbol(varName) >= goal,"Y","N"))

data %>%
  ggplot(aes(x = md, y = !!as.symbol(varName),color = fi)) +
  scale_colour_manual(values = c("white","springgreen3")) +
  geom_bar(stat = "identity", fill = "dodgerblue4", alpha = .6) +
  geom_text(aes(label = paste(round(!!as.symbol(varName)*100),"%",sep = ""), hjust = "right"), size = 2)+
  coord_flip() +
  labs(title = varName) + 
  theme_classic() + 
  theme(axis.line.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text = element_text(color = "black"),
        axis.title.y=element_blank(),
        axis.title.x=element_blank(),
        legend.position = "none", )  +
  scale_y_continuous(labels = scales::percent,
                     limits = c(0,1),
                     position = "right") + 
  geom_hline(yintercept = mean(dataValues), color="grey",
             linetype = "dashed") +
  geom_hline(yintercept = goal, color = "springgreen3", linetype = "dashed") +
  geom_text(aes(y = mean(dataValues), x = 0),
            label = paste("Average = ",round(mean(dataValues)*100,2),"%",sep = ""), color = "black") + 
  geom_text(aes(y = goal, x = length(dataValues)+1),
            label = paste(goal*100,"% Goal",sep = ""), color = "springgreen4") + 
  scale_x_discrete(expand = expansion(add = 1.8)) 
}

```

# {.tabset .tabset-fade}

## Analysis

### Overview
This analysis uses CPR case data from the *ZOLL* to evaluate code blue response efficiency. The data was collected from the SICU High Performance Code Team binder, and there are `r nrow(zollData)` CPR cases ranging from `r min(zollData$Date)` to `r max(zollData$Date)`. The primary goals of this PACE project are to:  
    
  * Establish a code blue performance baseline
  * Gain insight to what areas of CPR techniques are lacking
  * Educate fellow staff members  

### Data Summary  

```{r echo=FALSE, message=FALSE, warning=FALSE}
summaryTbl <- zollData %>%
  summarise(`CPR Cases` = n(),
            `Avg Compresion Depth (inches)` = round(mean(`Mean Compresion Depth`, na.rm = TRUE),2),
            `Avg Compression Rate (comp/min)` = round(mean(`Mean Compression Rate`, na.rm = TRUE),2),
            `Avg Time in CPR` = round(mean(`Time in CPR`, na.rm = TRUE),2),
            `Avg Time in Compressions` = round(mean(`Time in Compressions Prop`, na.rm = TRUE),4),
            `Avg Compressions in Target` = round(mean(`Compressions in Target`, na.rm = TRUE),4),
            `Avg Depth in Target` = round(mean(`Depth In Target Prop`, na.rm = TRUE),4),
            `Avg Rate in Target` = round(mean(`Rate in Target Prop`, na.rm = TRUE),4)) %>%
  mutate(`Avg Time in CPR` = paste(floor(as.numeric(`Avg Time in CPR`)/60),":", str_pad(string = as.numeric(`Avg Time in CPR`)%%60,width = 2,side = "left",pad = "0"), sep = "")) %>%
  rename(`Avg Time in CPR (min:sec)` = `Avg Time in CPR`)

summaryTbl %>%
  datatable(rownames = FALSE,filter = 'none',editable = FALSE,
            options = list(
  searching = FALSE,
  ordering = FALSE,
  paging = FALSE,
  bInfo = FALSE,
  columnDefs = list(list(className = 'dt-center', targets = 0:7))
)) %>% 
  formatPercentage(columns = c(5,6,7,8), digits = 2)

```

```{r warning=FALSE, message=FALSE, echo=FALSE,fig.height=4, out.width = '100%'}

plotSum <- summaryTbl %>% select(`Avg Compressions in Target`, `Avg Depth in Target`,
                                 `Avg Rate in Target`) %>%
  gather("Measure", "Value") %>%
  mutate(
  fi = if_else(Value >= .8,"Y","N")
  )

plotSum %>%
  ggplot(aes(Measure, Value, group = Measure, color = fi)) +
  scale_colour_manual(values = c("white","springgreen3"))+
  geom_bar(stat = "identity", fill = "dodgerblue4", alpha = .6) +
  geom_text(aes(label = paste(round(Value*100),"%",sep = ""), vjust = 1), size = 3) + 
  theme_classic() + 
  theme(axis.line.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text = element_text(color = "black"),
        axis.title.y=element_blank(),
        axis.title.x=element_blank(),
        legend.position = "none", )  +
  scale_y_continuous(labels = scales::percent,
                     limits = c(0,1),
                     position = "left") +
  geom_hline(yintercept = .8, color = "springgreen3", linetype = "dashed")  + 
  geom_text(aes(y = .85, x = 1),
            label = paste(.8*100,"% Goal",sep = ""), color = "springgreen4") +
  labs(title = "Overall Performance")
  

```


### Difference by Duration?


```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=4, out.width = '100%'}

pd <- zollData %>% select(`Time in CPR`, `Compressions in Target`, `Depth In Target Prop`,
                    `Rate in Target Prop`, record) %>%
  mutate(`Time in CPR` = as.numeric(`Time in CPR`)/60) %>%
  gather(key = "Measure", value = "Value", c(-`Time in CPR`,-record)) %>%
  mutate(
  fi = if_else(Value >= .8,"Y","N")
  ) %>%
  mutate(
  `CPR Duration` = case_when(
    as.numeric(`Time in CPR`) < 10 ~ "Under 10 Mins",
    TRUE ~ "Over 10 Mins"
  ),
  `CPR Duration` = factor(`CPR Duration`, levels = c("Under 10 Mins", "Over 10 Mins"))
) 
pd %>%
  ggplot(aes(x = `Time in CPR`, y = Value, color = fi, fill = `CPR Duration`)) + 
  scale_colour_manual(values = c("black","springgreen3")) +
  scale_fill_manual(values = c("cyan","yellow")) +
  geom_point(shape = 21) +
  facet_grid(cols = vars(Measure)) + 
  theme(axis.line.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text = element_text(color = "black"),
        axis.title.y=element_blank(),
        axis.title.x=element_blank(),
        legend.position = "bottom")  +
  scale_x_continuous(breaks = c(5,10,15,20,30,40)) +
  xlab("Minutes") + 
  geom_hline(yintercept = .8, color = "springgreen3", linetype = "dashed") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     breaks = c(0,.25,.5,.75,.8,1)) + 
  xlab("Minutes") +
  guides(color = FALSE)

```


```{r echo=FALSE, message=FALSE, warning=FALSE}
summaryTbl2 <- zollData %>% mutate(
  `CPR Duration` = case_when(
    as.numeric(`Time in CPR`) < 600 ~ "Under 10 Mins",
    TRUE ~ "Over 10 Mins"
  ),
  `CPR Duration` = factor(`CPR Duration`, levels = c("Under 10 Mins", "Over 10 Mins"))
) %>% group_by(`CPR Duration`) %>%
  summarise(`CPR Cases` = n(),
            `Avg Compresion Depth (inches)` = round(mean(`Mean Compresion Depth`, na.rm = TRUE),2),
            `Avg Compression Rate (comp/min)` = round(mean(`Mean Compression Rate`, na.rm = TRUE),2),
            `Avg Time in CPR` = round(mean(`Time in CPR`, na.rm = TRUE),2),
            `Avg Time in Compressions` = round(mean(`Time in Compressions Prop`, na.rm = TRUE),4),
            `Avg Compressions in Target` = round(mean(`Compressions in Target`, na.rm = TRUE),4),
            `Avg Depth in Target` = round(mean(`Depth In Target Prop`, na.rm = TRUE),4),
            `Avg Rate in Target` = round(mean(`Rate in Target Prop`, na.rm = TRUE),4)) %>%
  mutate(`Avg Time in CPR` = paste(floor(as.numeric(`Avg Time in CPR`)/60),":", str_pad(string = round(as.numeric(`Avg Time in CPR`)%%60),width = 2,side = "left",pad = "0"), sep = "")) %>%
  rename(`Avg Time in CPR (min:sec)` = `Avg Time in CPR`)

summaryTbl2 %>%
  datatable(rownames = FALSE,filter = 'none',editable = FALSE,
            options = list(
  searching = FALSE,
  ordering = FALSE,
  paging = FALSE,
  bInfo = FALSE,
  columnDefs = list(list(className = 'dt-center', targets = 0:8))
)) %>% 
  formatPercentage(columns = c(6,7,8,9), digits = 2)

```


### CPR Results by Case  {.tabset .tabset-fade .tabset-pills} 

#### Compressions in Target

```{r warning=FALSE, message=FALSE, echo=FALSE,fig.height=4, out.width = '100%'}
percentBars("Compressions in Target")
```


#### Depth in Target

```{r warning=FALSE, message=FALSE, echo=FALSE,fig.height=4, out.width = '100%'}
percentBars("Depth In Target Prop", newName = "Depth in Target")
```


#### Rate in Target

```{r warning=FALSE, message=FALSE, echo=FALSE,fig.height=4, out.width = '100%'}
percentBars("Rate in Target Prop", newName = "Rate in Target")
```


#### Time in Compressions

```{r warning=FALSE, message=FALSE, echo=FALSE,fig.height=4, out.width = '100%'}
percentBars("Time in Compressions Prop", newName = "Time in Compressions", goal = .92)
```


#### Data
```{r echo=FALSE, message=FALSE, warning=FALSE}

zollData %>% select(-record, -md) %>%
  datatable(rownames = FALSE) %>%
  formatPercentage(columns = c(9,10,15,16,17,21,22,23), digits = 2)


```



## *ZOLL* Instructions

  * Device Use
  * Software Use
  * Reporting  
  
## AHA Guidlines  

  * Overview
  * Flowcharts
  * Useful Links  

## Survey Results

<center><iframe src="https://www.surveymonkey.com/stories/SM-PV5Y7W22/" width="900" height="780" style="border: none;"></iframe></center>


## Education Sign-Off

<center><iframe src="https://docs.google.com/forms/d/e/1FAIpQLSeJdgBJVK6nQrKK3-3GBXcVsZnVu24YGokEhBCeeXQkfwgTJA/viewform?embedded=true" width="640" height="641" frameborder="0" marginheight="0" marginwidth="0">Loading…</iframe></center>





